DIAGNOSTIC SUPPORT OF SKIN LESION CLASSIFICATION USING CNN AND SOFT ATTENTION

### 2022-08-11 MDPI/Sensor Paper/template.tex
Update Research Paper

In the previous paper\cite{03358}, the image data is augmented for all class, the number of image increase to 18015 images. Since, this data is imbalanced, using augmented data may cause the problem of well classify on the majority of class. In this paper, instead of augmenting data, metadata is used. The way of processing metadata is discussed in MetaData section. Images in this data set has the type of $RGB$ and shape of (450, 600). However, Each backbone need the different input size of image as well as the range of pixel value. DenseNet201\cite{06993} require the input pixels values are scaled between $0$ and $1$ and each channel is normalized with respect to the ImageNet data set. In Resnet50 and Resnet152\cite{03385}\cite{05027}, the images are converted from $RGB$ to $BGR$, then each color channel is zero-centered with respect to the ImageNet data set, without scaling. InceptionResNetV2\cite{11946}, on the other hand, will scale input pixels between $-1$ and $1$. Similarly, three versions of MobileNet\cite{04861}\cite{04381}\cite{02244}, NasNetMobile and NasNetLarge\cite{07012} require the input pixel is in range of $-1$ and $1$.

\subsubsection{Metadata}
The HAM10000 data set\cite{10417} also contain the metadata of patient including gender, age, and the capturing position. During the data exploration term, the age category miss 57 data points, which is decided to remove this 57 samples. In the gender and capturing position category contain some samples of unknown. Instead of removing, these "unknowns" data points is kept and considered as "prefer not to say". Besides, the label of the whole data is preprocessed into one-hot vector.
\subsection{Model Schema}
\subsubsection{Input Schema}
Using metadata as another input is not new. In paper\cite{03910}, they decide to keep the missing value and set its value to $0$. The sex and anatomical site are categorical encoded. The age, on the other hand is numerical normalized. After processing, the metadata is fed into a two-layer neural network with 256 neurons each. Each layer contains batch normalization, a ReLU\cite{08375} activation, and dropout with $p = 0.4$. The network’s output is concatenated with the CNN’s feature vector after global average pooling. Especially, they use a simply data augmentation strategy to address the problem of missing values in metadata. During training, they randomly encode each property as missing with a probability of $p = 0.1$.

>>>>

In the previous research\cite{03358}, the image data is augmented for all class, the number of image increase to 18015 images. Since, this data is imbalanced, using augmented data may cause the problem of well classify on the classes almostly taking the number of samples. In this paper, instead of augmenting data, metadata is used. The way of processing metadata is discussed in MetaData section. Images in this data set has the type of $RGB$ and shape of (450, 600). However, Each backbone need the different input size of image as well as the range of pixel value. DenseNet201\cite{06993} require the input pixels values are scaled between $0$ and $1$ and each channel is normalized with respect to the ImageNet data set. In Resnet50 and Resnet152\cite{03385}\cite{05027}, the images are converted from $RGB$ to $BGR$, then each color channel is zero-centered with respect to the ImageNet data set, without scaling. InceptionResNetV2\cite{11946}, on the other hand, will scale input pixels between $-1$ and $1$. Similarly, three versions of MobileNet\cite{04861}\cite{04381}\cite{02244}, NasNetMobile and NasNetLarge\cite{07012} require the input pixel is in range of $-1$ and $1$.

\subsubsection{Metadata}
The HAM10000 data set\cite{10417} also contain the metadata of patient including gender, age, and the capturing position as well as the test data set containing 857 images. During the data exploration term, the age category miss 57 data points, which is decided to remove this 57 samples. In the gender and capturing position category contain some samples of unknown. Instead of removing, these "unknowns" data points is kept and considered as "prefer not to say". Besides, the label of the whole data is preprocessed into one-hot vector.
\subsection{Model Schema}
\subsubsection{Input Schema}
Using metadata as another input is not new. In paper\cite{03910}, they decide to keep the missing value and set its value to $0$. The sex and anatomical site are categorical encoded. The age, on the other hand is numerical normalized. After processing, the metadata is fed into a two-layer neural network with 256 neurons each. Each layer contains batch normalization, a ReLU\cite{08375} activation, and dropout with $p = 0.4$. The network’s output is concatenated with the CNN’s feature vector after global average pooling. Especially, they use a simply data augmentation strategy to address the problem of missing values in metadata. During training, they randomly encode each property as missing with a probability of $p = 0.1$.
